Apache Flink\texttrademark: Stream and Batch Processing in a Single Engine

### 2016-05-26 paper.tex
shrink to 11 pages
foobar
Updates from ShareLaTeX

@@

\author{Paris Carbone\textsuperscript{$\dagger$} \\ Asterios Katsifodimos\textsuperscript{*} \\\\ \small{ \textsf{\small \textsuperscript{$\dagger$}KTH \& SICS Sweden}} \\ \small \href{parisc,haridi@kth.se}{parisc,haridi@kth.se}
\and Stephan Ewen\textsuperscript{$\ddagger$} \\ Volker Markl\textsuperscript{*} \\\\ \small \textsf{\textsuperscript{$\ddagger$}Data Artisans GmbH} \\ \small \href{first@data-artisans.de}{first@data-artisans.de}
\and Seif Haridi\textsuperscript{$\dagger$} \\ Kostas Tzoumas\textsuperscript{$\ddagger$} \\\\ \small \textsf{\textsuperscript{*}TU Berlin} \\ \small \href{fist.last@tu-berlin.de}{first.last@tu-berlin.de}
%
\vspace{-5mm}
}

@@

@@

\para{Batch Processing.} Apache Hadoop is one of the most popular open-source systems for large-scale data analysis that is based on the MapReduce paradigm~\cite{DBLP:journals/cacm/DeanG08}. Dryad~\cite{isard2007dryad} introduced embedded user-defined functions in general DAG-based dataflows and was enriched by SCOPE~\cite{scopeOptimizer}, which a language and an SQL optimizer on top of it. Apache Tez~\cite{saha2015apache} can be seen as an open source implementation of the ideas proposed in Dryad. MPP databases \cite{dewitt1990gamma}, and recent open-source implementations like Apache Drill and Impala \cite{kornacker2015impala}, restrict their API to SQL variants. Similar to Flink, Apache Spark \cite{DBLP:conf/hotcloud/ZahariaCFSS10} is a data-processing framework that implements a DAG-based execution engine, provides an SQL optimizer, performs driver-based iterations, and treats stream computations as micro-batches. In contrast, Flink is the only system that incorporates
\begin{inparaenum}[i)]
  \item a distributed dataflow runtime that exploits pipelined streaming execution for batch and stream workloads,
  \item exactly-once state consistency through lightweight checkpointing,
  \item efficient, native iterative processing,
  \item sophisticated window semantics, supporting out-of-order processing.
\end{inparaenum}

\vspace{-3mm}
\section{Conclusion}
\label{sec:conclusions}
In this paper we presented Apache Flink, a platform that implements a universal dataflow engine designed to perform both stream and batch analytics. Flink's dataflow engine treats operator state and logical intermediate results as first-class citizens, and is used by both the batch and a data stream APIs, with different parameters. The streaming API that is built on top of  Flink's streaming dataflow engine provides the means to keep recoverable state and to partition, transform, and aggregate windows of a data stream. While batch computations are, in theory, a special case of a streaming computations, Flink treats them specially, by optimizing their execution with a novel query optimizer, and by implementing blocking operators that gracefully spill to disk in the absence of memory.

{
\small
\bibliographystyle{abbrv}
\bibliography{references}
}

>>>>

\usepackage[
backend=biber
% style=alphabetic,
% sorting=abbrv
]{biblatex}

\renewbibmacro{in:}{}

\addbibresource{references.bib}
\renewcommand{\bibfont}{\small} % or any other  appropriate font command

@@

\author{Paris Carbone\textsuperscript{$\dagger$} \\ Asterios Katsifodimos\textsuperscript{*} \\\\ \small{ \textsf{\small \textsuperscript{$\dagger$}KTH \& SICS Sweden}} \\ \small \href{parisc,haridi@kth.se}{parisc,haridi@kth.se}
\and Stephan Ewen\textsuperscript{$\ddagger$} \\ Volker Markl\textsuperscript{*} \\\\ \small \textsf{\textsuperscript{$\ddagger$}data Artisans} \\ \small \href{first@data-artisans.com}{first@data-artisans.com}
\and Seif Haridi\textsuperscript{$\dagger$} \\ Kostas Tzoumas\textsuperscript{$\ddagger$} \\\\ \small \textsf{\textsuperscript{*}TU Berlin} \\ \small \href{fist.last@tu-berlin.de}{first.last@tu-berlin.de}
%
\vspace{-5mm}
}

@@

\para{Batch Processing.} Apache Hadoop is one of the most popular open-source systems for large-scale data analysis that is based on the MapReduce paradigm~\cite{DBLP:journals/cacm/DeanG08}. Dryad~\cite{isard2007dryad} introduced embedded user-defined functions in general DAG-based dataflows and was enriched by SCOPE~\cite{scopeOptimizer}, which a language and an SQL optimizer on top of it. Apache Tez~\cite{saha2015apache} can be seen as an open source implementation of the ideas proposed in Dryad. MPP databases \cite{dewitt1990gamma}, and recent open-source implementations like Apache Drill and Impala \cite{kornacker2015impala}, restrict their API to SQL variants. Similar to Flink, Apache Spark \cite{DBLP:conf/hotcloud/ZahariaCFSS10} is a data-processing framework that implements a DAG-based execution engine, provides an SQL optimizer, performs driver-based iterations, and treats stream computations as micro-batches. In contrast, Flink is the only system that incorporates
\begin{inparaenum}[i)]
  \item a distributed dataflow runtime that exploits pipelined streaming execution for batch and stream workloads,
  \item exactly-once state consistency through lightweight checkpointing,
  \item native iterative processing,
  \item sophisticated window semantics, supporting out-of-order processing.
\end{inparaenum}

@@

\vspace{-4mm}
\section{Conclusion}
\vspace{-2mm}
\label{sec:conclusions}
In this paper we presented Apache Flink, a platform that implements a universal dataflow engine designed to perform both stream and batch analytics. Flink's dataflow engine treats operator state and logical intermediate results as first-class citizens, and is used by both the batch and a data stream APIs, with different parameters. The streaming API that is built on top of  Flink's streaming dataflow engine provides the means to keep recoverable state and to partition, transform, and aggregate windows of a data stream. While batch computations are, in theory, a special case of a streaming computations, Flink treats them specially, by optimizing their execution with a novel query optimizer, and by implementing blocking operators that gracefully spill to disk in the absence of memory.

% {
% \small
% \bibliographystyle{abbrv}
% \bibliography{references}
% }
\printbibliography
